Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-11-14 paper/paper1/ms.tex
Add some text on other archival data sources

>>>>

\subsection{Gaia DR3}
HAT-P-67A has a parallax of \censorbox{x} in \emph{Gaia} DR3,

\subsection{Other archives}
We searched for observations of HAT-P-67 in public archives.  It has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 $\AA$.  It has 26 photometry points from \emph{Pan-STARRS} spread across its 5 filters.  The other archival observations have been previously reported by \censorbox{Zhou et al. 2017}, including Keck HIRES, Keck NIRC2, and WIYN High-Resolution Infrared Camera.  The northern source does not appear in ESO archives, nor the Gemini Archive, and it is not publicly accessible in the Zwicky Transient Factory (ZTF) archive.  It was not targeted by Spitzer or Hubble.
